\section{Typed Schema Definition}\label{sec:syntax}

TA3 is developing a versioned and typed schema that codifies the above
conceptual model. The actual data model will necessarily evolve based
on the TA1-TA2 discussions expected in the coming months.  The schema
definition will evolve in parallel to match the latest version of the
data model.

The schema is specified using the Apache Avro Interface Description
Language (IDL) language. Avro IDL is a high-level language for
authoring Avro schemata. It provides a familiar feel for developers in
that it is similar to common programming languages like Java, C++, and
Python. Also, it is similar to IDLs in other serialization
frameworks such as Thrift and Protocol Buffers. Avro provides a tool
to convert the Avro IDL specification into an Avro schema in JSON
format, which is used by Avro serialization frameworks for automatic
serialization and deserialization of objects that conform to the schema.
Avro (and the TA3 APIs) additionally provide the tools for automatic 
syntax checking to verify the data conforms to the typed schema.

Both the schema and this documentation are kept in the same git repository 
and will evolve together. The latest development snapshot containing the evolving schema is
in a git repository shared with the rest of the TC team at the following URL 
\href{https://git.tc.bbn.com/bbn/ta3-serialization-schema/tree/master/avro}{https://git.tc.bbn.com/bbn/ta3-serialization-schema/tree/master/avro}. 
Look for the latest version $xx$ of the schema file {\em CDMxx.avdl}.
